On the Dynamics of Anthropomorphism in Robotics \thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}

### 2013-05-22 anthropomorphism.tex
Rewrite intro of model + added section to introduce the 3 phases

\section{Anthropomorphic Design and Anthropomorphism}
\label{intro}

@@

	Why does anthropomorphic design seem to be so popular in HRI? Amongst others, a human-like shape and human-social characteristics of a robot aim to enable effective and natural interaction between humans and robots. As robots are generally something unfamiliar and new to humans, the underlying argumentation is that when a robot has a human-like shape and displays human social cues, it is easier for people to interact with it. A robot's anthropomorphic design suggests to the human user to understand and treat it to some extend similar to a human, thus in a social manner. This behavior has been extensively studied in HCI and is explained by the \emph{Media Equation Theory}, which states that people's interactions with computers, television, and new media are fundamentally social and natural, just like interactions in real life \cite{reeves_media_1996}. Since robots are physically embodied agents, it is consequently very likely that people respond socially to them. The anthropomorphic design in a robot further encourages a person to ascribe / attribute human characteristics to it (e.g. intention, emotions, personality). To this end, anthropomorphic design of robots aims to make the system understandable, thus predictable, and acceptable. The conclusion builds on the assumption that humans prefer to interact with machines (and robots) in the same way they interact with humans \cite{fong_survey_2003} because they are familiar to these kind of interactions. The implicit social mechanism which is exploited, is called \textbf{anthropomorphism}. It describes the phenomenon of a person ascribing human-like characteristics (e.g. beliefs, intentions, personality) to a non-human artifact, such as a robot. Anthropomorphism also concerns a person's reasoning about a non-human agent as if that agent were human-like (\textit{i.e.} a cognitive process without the action of making a verbal statement with attribution, for instance). In robotics, this social phenomenon is enhanced by using anthropomorphic forms in the design of robots, thus these two aspects are closely related to each other.

@@

% vertical axis
\draw[->] (0,0) -- (0,6) node[anchor=east] {};
\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphism};

@@

We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature that once observed during a short-term interaction reflects a sustaining social effect. So far, the HRI community has not investigated how anthropomorphism in human-robot interactions evolves over time (during the process of adopting a robot, for instance). However, based on an extensive literature review and our own work, we believe that the social phenomenon will not always be the same but evolve over time, with growing interaction and experience with the robot. We would like to present an extension to the understanding of anthropomorphism in HRI which takes time / interaction / experience / familiarization into account. Consequently, we suggest to understand anthropomorphism in HRI as a dynamic process, which is likely to change over time and with growing user experience with the robot (which we assume comes along with a familiarization and better understanding of the robot). This viewpoint also considers the so called \textit{novelty effect} which has been observed during long-term studies with innovative technologies and robots. In the following, we present our understanding of the dynamics of anthropomorphism and try to model this process as a function of time and growing experience (see Figure \ref{fig:dynamics}).

\subsection{The Initial Capital of Anthropomorphism}
\label{sec:7.1}

@@

\subsection{Anthropomorphism during Initialization Phase}
\label{sec:7.2}

(\textit{INITIALIZATION})

\subsection{Anthropomorphism during Familiarization Phase}
\label{sec:7.3}

\subsection{Anthropomorphism during Stabilization Phase}
\label{sec:7.4}

>>>>

\section{Anthropomorphic Design and Anthropomorphism}
\label{sec:intro}

@@

     Why does anthropomorphic design seem to be so popular in HRI? Amongst others, a human-like shape and human-social characteristics of a robot aim to enable effective and natural interaction between humans and robots. As robots are generally something unfamiliar and new to humans, the underlying argumentation is that when a robot has a human-like shape and displays human social cues, it is easier for people to interact with it. A robot's anthropomorphic design suggests to the human user to understand and treat it to some extend similar to a human, thus in a social manner. This behavior has been extensively studied in HCI and is explained by the \emph{Media Equation Theory}, which states that people's interactions with computers, television, and new media are fundamentally social and natural, just like interactions in real life \cite{reeves_media_1996}. Since robots are physically embodied agents, it is consequently very likely that people respond socially to them. The anthropomorphic design in a robot further encourages a person to ascribe / attribute human characteristics to it (e.g. intention, emotions, personality). To this end, anthropomorphic design of robots aims to make the system understandable, thus predictable, and acceptable. The conclusion builds on the assumption that humans prefer to interact with machines (and robots) in the same way they interact with humans \cite{fong_survey_2003} because they are familiar to these kind of interactions. \hl{The implicit social mechanism which is exploited, is called \textbf{anthropomorphism}}\fxfatal{Discuss also \emph{anthropomorphic effects} as the observable part of anthropomorphism}. It describes the phenomenon of a person ascribing human-like characteristics (e.g. beliefs, intentions, personality) to a non-human artifact, such as a robot. Anthropomorphism also concerns a person's reasoning about a non-human agent as if that agent were human-like (\textit{i.e.} a cognitive process without the action of making a verbal statement with attribution, for instance). In robotics, this social phenomenon is enhanced by using anthropomorphic forms in the design of robots, thus these two aspects are closely related to each other.

@@

% vertical axis
\draw[->] (0,0) -- (0,6) node[anchor=east] {};
\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};

@@

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time (during the process of
\emph{adopting} a robot, for instance): we propose to go beyond the traditional
perception of anthropomorphism in robotics as a static feature that once
observed during a short-term interaction reflects a sustaining social effect.
Based on an extensive literature review and our own work \fxfatal{Summarize
these findings in a specific section!}, we believe that the social phenomenon
is not always be the same but evolve over time, along with growing interaction
and experience with the robot.

The model of anthropomorphism we propose (Figure~\ref{fig:dynamics}) represents
how the level of anthropomorphic effects (\ie observable manifestations of
anthropomorphism, as defined at section~\ref{sec:intro}) evolves over a
long-term human-robot interaction. By long-term interaction, we mean direct
(non-mediated), repeated interaction with the same robot, over (at least) several
days. The nature of the interaction (goal-directed, entertainment,...) may vary.

The model takes into account the duration of the interaction, the nature of the
interaction, as well as acquired experience and familiarization mechanisms: We
also propose to formally introduce a so-called \emph{novelty effect} that
models the first phase of human-robot interaction, and during which specific
anthropomorphic effect are observed.

\subsection{Three phases}
\label{sec:phases}

We distinguish three main phases that describe the evolution of the
anthorpomorphic effects in a long-term human-robot interaction. They are
depicted in different shades on Figure~\ref{fig:dynamics}.

First, the \emph{initialization} phase. During this short phase (from a couple
of seconds to a couple of hours), we observe an increased level of
antrophomorphism, from an \emph{initial capital of anthropomorphism}
(detailled in the next section) and a peak of antropomorphic manifestations
that correspond to the maximum of the \emph{novelty effect}.
Section~\ref{sec:initialization} details this first phase.

The second phase, \emph{familiarization}, lasts longer (up to several days) and
models the process of the human getting acquainted to the robot: by observation
and interaction, the human builds a model of the robot's behaviour that allows
him/her to predict the robot's actions. We observe a decrease of
anthropomorphic effects during this phase, that we explain by the acquired
ability to predict the behaviour of the robot: the initial apparent behavioural
complexity vanishes, and the robot is considered more and more as a machine.
Section~\ref{sec:familiarization} discusses the second phase.

The last phase is the \emph{stabilization} phase. The level of anthrpomorphic
effects tends to stabilize over a longer time, to reach a \emph{stabilized
level of anthropomorphism} (SLA). The SLA may be null (no anthropomorphic
effects observed anymore), but it may also remain at an higher level.  This
third phase, as well as the \emph{stabilized level of anthropomorphism}, are
discussed in section~\ref{sec:stabilization} below.

\subsection{Initial Capital of Anthropomorphism}
\label{sec:ica}

@@

\subsection{Anthropomorphism during Initialization Phase}
\label{sec:initialization}

\paragraph{The Novelty Effect}
\label{sec:noveltyeffect}

\subsection{Anthropomorphism during Familiarization Phase}
\label{sec:familiarization}

\paragraph{Disruptive Behaviours}

\subsection{Anthropomorphism during Stabilization Phase}
\label{sec:stabilization}

\paragraph{Stabilized Level of Anthropomorphism (SLA)}
